Next Trippy Structures\thanks{Supported by organization x.}

### 2019-06-11 paper.tex
Update on Overleaf.

The only query for which \ttctr~is clearly preferred over \ctr~is \texttt{board\_X}, with any restriction, as can be seen in the Figure~\ref{fig:board}. Both for \texttt{board\_X} and \texttt{board\_X$_{L}$}, \ttctr~takes on average less than one microsecond per query, as the only operations needed are two constant time $select$ over the bitvector \texttt{D} from the \texttt{CSA}, while \ctr~needs to subtract the occurrences of $X\$$ (as those are alighting stops, not boarding), for which $\Psi$ must be accessed. This advantage is carried on the queries with time restrictions as well.

\begin{figure}[hbt!]
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/board.eps}
\vspace{-12pt}
\caption{\footnotesize (a)}
\vspace{-12pt}
\end{subfigure}%
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/board_t.eps}
\vspace{-12pt}
\caption{\footnotesize (b)}
\vspace{-12pt}
\end{subfigure}
\caption{Comparison of \texttt{board\_X$_{LT}$} queries, with all variants (a) and also with all variants of T-Matrix (b). Note the logarithmic scale in (b), as well as the measurements in nanoseconds}
\label{fig:board}
\end{figure}

>>>>

The only query for which \ttctr~is clearly preferred over \ctr~is \texttt{board\_X}, with any restriction, as can be seen in the Figure~\ref{fig:board}a. Both for \texttt{board\_X} and \texttt{board\_X$_{L}$}, \ttctr~takes on average less than one microsecond per query, as the only operations needed are two constant time $select$ over the bitvector \texttt{D} from the \texttt{CSA}, while \ctr~needs to subtract the occurrences of $X\$$ (as those are alighting stops, not boarding), for which $\Psi$ must be accessed. This advantage is carried on the queries with time restrictions as well.

\begin{figure}[hbt!]
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/board.eps}
\vspace{-12pt}
\caption{\footnotesize (a)}
\vspace{-12pt}
\end{subfigure}%
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/board_t.eps}
\vspace{-12pt}
\caption{\footnotesize (b)}
\vspace{-12pt}
\end{subfigure}
\caption{Comparison of \texttt{board\_X$_{LT}$} queries, with all variants (a) and also with all variants of \acumm~(b). Note the logarithmic scale in (b), as well as the measurements in nanoseconds}
\label{fig:board}
\end{figure}

When comparing the best performing configuration of \ttctr~to the different variants of \acumm~discussed in Section~\ref{sec:acumm}, we can observe wildly different results in Figure~\ref{fig:board}b depending on the variant of the \texttt{board\_X} query used. The biggest difference is observed when comparing queries that filter by time, which use the \textt{WMT} in \ttctr, while for any variant of \acumm~solves it in a small number of constant time operations. Another evident difference occurs between queries that
